Phylogenetics and the human microbiome.

### 2013-05-01 sbreview.tex
minor changes

The human microbiome is the collection of cells that live inside and on humans.
The Human Microbiome Project (HMP) and the Metagenomics of the Human Intestinal Tract (MetaHIT) consortia have advanced human microboime research by generating thousands of 16s surveys and terabases of metagenomic data on the human microbiome, as well as funding bioinformatics and statistical development.
In this paper I review the impact of phylogenetics and tree-thinking on the methods used in the analysis of this data, as well as describing current challenges for phylogenetics coming from this type of work.

>>>>

The human microbiome is the collection of microbes that live inside and on humans.
The Human Microbiome Project (HMP) and the Metagenomics of the Human Intestinal Tract (MetaHIT) consortia have advanced human microboime research by generating thousands of 16s surveys and terabases of metagenomic data on the human microbiome, as well as funding bioinformatics and statistical development.
In this talk I will review the impact of phylogenetics and tree-thinking on the methods used in the analysis of this data, as well as describing current challenges for phylogenetics coming from this type of work.
